Asteroid project summary

### 2022-01-21 summaries/21-11/21-11.tex
Finished oblateness-differ

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{oblateness.pdf}
  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet. Linear best fit lines (black, dotted) are plotted over the 1- and 2-$\sigma$ uncertainties. Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
  \label{fig:oblateness}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{oblateness.pdf}
  \includegraphics[width=0.4\textwidth]{oblateness-differ.pdf}
  \caption{(\textit{Left}) Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet. Linear best fit lines (black, dotted) are plotted over the 1- and 2-$\sigma$ uncertainties. (\textit{Right}) The deviation of fit parameters from the true parameters when a zero oblateness model is fitted to data with oblateness $\epsilon$. Also shown in both figures are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
  \label{fig:oblateness}
\end{figure}

@@

The second figure of figure \ref{fig:oblateness} shows divergence of best-fit parameters from the true values when an incorrect oblateness is used. Specifically, the figure shows the difference between parameter values extracted via a model with $\epsilon=0$ and the true parameter values used to generate data with oblateness $\epsilon \neq 0$. The uncertainty on fit parameters is roughly constant over variations in $\epsilon_\textrm{true}$, but very quickly (even for $\epsilon_\textrm{true} = 10^{-4}$) the fit values become inconsistent with the true values. The observational uncertainty used here was the benchmark value, but even if observational uncertainty were increased by a factor of 10 (resulting in a factor of 10 increase in best-fit uncertainty --- see section \ref{sec:probe-sigma}) the figure shows that the best fit results would still exclude the true results by $>2\sigma$ if the oblateness of Earth were approximated as zero. For 100-fold increase in uncertainty, mismodeling Earth's oblateness would not lead to by $2\sigma$  divergence, but mismodeling Jupiter would.
